### 2025-02-26 manuscript/manuscript.qmd
live editing the MS
manuscript: update classification reporting
fix issue in reporting of splits

The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), though $MCC$ shows differences on averages based on the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754). Conversely, model classes differ significantly (_Q_(3) = 4.22, _p_ = 0.239). Specifically, neural networks outperform all other model types ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728). Studies did not differ based on whether stimuli comprised one or multiple genres (_Q_(1) = 0.12, _p_ = 0.7324), or whether studies employed binary or multi-class models (_Q_(1) = 0.03, _p_ = 0.8694).

NOTE. Model classes do not seem to differ significantly!?

@@

<!-- ### Feature definition -->

>>>>

The number of features (as classified into under 30, between 30 and 300, and above 300 features) analyzed does not significantly impact results (_Q_(2) = 3.91, _p_ = 0.1419), despite $MCC$s showing average differences according to the number of features (< 30 F: $MCC$ = 0.9293; 30-300 F: $MCC$ = 0.8458; >300 F: $MCC$ = 0.7754). Similarly, the class of model did not differ significantly (_Q_(3) = 4.22, _p_ = 0.239) despite neural networks attaining highest average performance ($MCC$ = 0.9307), followed by SVMs ($MCC$ = 0.870) and tree-based methods ($MCC$ = 0.854), then linear methods ($MCC$ = 0.728). Finally, neither single- vs. multigenre studies (_Q_(1) = 0.12, _p_ = 0.7324), nor binary vs. multi-class models (_Q_(1) = 0.03, _p_ = 0.8694) differed significantly.

@@

<!-- ### Feature definition/validations -->
